\section*{Differences from Previous Work}
This work has not been previously published. It builds upon an earlier conference publication ``CAD and Routing Architecture for Interposer-Based Multi-FPGA Systems,'' A. Hahn Pereira and V. Betz, \textit{ACM Int. Symposium on FPGAs}, 2014, pp. 75 - 84, but greatly improves on and extends this earlier work.  Approximately 75\% of the material in this paper is entirely new methods and new results that are not in the conference paper; the remaining 25\% of the material (chiefly the Introduction, Background, some of the Architecture Models and the Placer Optimization subsection of CAD Enhancements) have been updated since the conference paper but cover the same basic material as the conference paper. In detail, new material includes:

\begin{itemize}
\item Partitioning is now included in the CAD flow. We investigate multiple ways to formulate the partitioning problem for interposer-based FPGAs and compare the results to CAD flows without partitioning. All of Section V of the paper (4 pages) is completely new material vs. the conference paper.

\item Section III, Architecture Models has been expanded vs. the conference paper, and the method of modeling the architecture in the CAD tools is new.  Section III.D is completely new and Section III.E uses a different method than the conference paper and has been rewritten and expanded.

\item Section IV, CAD enhancements contains mostly new material vs. the conference paper. The router enhancements section (IV.B) is entirely new, while the placement enhancement section (IV.A) is shortened and the effectiveness of the enhancements section (IV.C) is new.

\item All of the architecture results have been re-run with the new CAD flow and architectural enhancements proposed in this paper, so all the results in Section VI are different and markedly better than those of the conference paper; this entire section has been re-written. Sections VI.A and VI.E investigate entirely new architecture questions proposed in this paper; there is no analog to these sections in the earlier conference paper.

\item The Introduction, Background and Conclusions (Section I, II and VII) have been updated to highlight the new results of this paper and to describe recent developments in commercial interposer-based FPGAs at 20 nm.
\end {itemize}

